---
title: "Making a PLINK formatted Map"
output: html_notebook
---

We started from the Torterau map, but now it would be nice to
make a map that was marker-focused so we can show how it can
be turned into a bin-focused sort of map that works with gscramble.

So, I want to make it something that is pretty close to what we get
from the bins, assuming uniform recombination within the bins.  

The way we will do this is we will turn the RecRates into something
that has a single column of positions, then we will bind_rows the
markers in there, and then we will fractionize recombination rates out
of those bins and things.

```{r}
library(tidyverse)
library(gscramble)
```


Reformatting the RecRates:
```{r}
r2 <- RecRates %>%
  select(-chrom_len, -end_pos) %>%
  rename(pos = start_pos)
```

Binding on the markers and sorting:
```{r}
mb <- bind_rows(r2, M_meta) %>%
  arrange(chrom, pos) %>%
  mutate(
    p2 = ifelse(is.na(rec_prob), NA, pos),
    p_up = p2,
    p_down = p2
  ) %>%
  fill(p_up, .direction = "up") %>%
  fill(p_down, .direction = "down")

# and then we need a function that will operate on chromomes
interval_rec_probs <- function(p, rp, pd, pu) {
  n <- length(p)
  ret <- rep(-99, n)
  i <- 1
  while(i <= n) {
    if(!is.na(rp[i])) {
      ret[i] <- rp[i]
    } else {
      tot <- pu[i] - pd[i]
      rtot <- rp[i - 1]
      ret[i - 1] <- rtot * (p[i] - p[i - 1]) / tot;
      flag = FALSE
      while(is.na(rp[i]) && i < n) {
        ret[i] <- rtot * (p[i + 1] - p[i]) / tot
        i <- i + 1
        flag = TRUE
      }
      if(flag) {
        i <- i - 1
      }
    }
    i <- i + 1
  }
  ret
}

filled_rates <- mb %>%
  group_by(chrom) %>%
  mutate(nrp = interval_rec_probs(pos, rec_prob, p_down, p_up), .after = rec_prob)

# and then once we have those we can just add them.
# this assumes that the marker is not at position 1.
get_marker_recombs <- function(p, r, v) {
  sum <- 0
  n <- length(p)
  ol <- sum(!is.na(v)) + 1
  m <- 1
  ret_p <- rep(NA, ol)
  ret_r <- rep(NA, ol)
  ret_v <- rep(NA, ol)
  
  ret_p[1] <- p[1]
  for(i in 1:n) {
    sum = sum + r[i]
    if(!is.na(v[i])) {
      ret_r[m] <- sum
      m <- m + 1
      ret_p[m] <- p[i]
      ret_v[m] <- v[i]
      sum <- 0
    }
  }
  tibble(
    pos = ret_p,
    var = ret_v,
    rec = ret_r
  )
}

close_to_done <- filled_rates %>%
  group_by(chrom) %>%
  dplyr::do(get_marker_recombs(p = .$pos, r = .$nrp, v = .$variant_id))

```

Now, we can check the sum of the recomb rates to make sure that we are close:
```{r}
close_to_done %>%
  group_by(chrom) %>%
  summarise(sum = sum(rec, na.rm = TRUE))
```

And we compare that to the sum of all the bins:
```{r}
RecRates %>%
  group_by(chrom) %>%
  summarise(sum = sum(rec_prob))
```

Which looks good.  We are going to miss some on the ends because
the chromosome extends beyond the last marker.

The last thing we need to do is shift the recombination rates by 1, because
in plink that is supposed to be the position of the marker in Morgans.

```{r}
ready_to_write <- close_to_done %>%
  group_by(chrom) %>%
  mutate(M = lag(rec)) %>%
  select(chrom, var, M, pos) %>%
  filter(!is.na(var)) %>% 
  mutate(M = cumsum(M)) %>%
  ungroup()

write_tsv(
  ready_to_write,
  file = "../inst/extdata/example-plink-with-morgans.map.gz", 
  col_names = FALSE
)
```



